PUT YOUR TITLE HERE

### 2023-03-16 code/process.Rmd
work on floats

@@

```{r}
d <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
                       sheet="aligned data", skip=1) |> 
  select(target_lastauthor_year, sensitivity, include,
         status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_raw_stat, same_dir, replication_N,
         replication_raw_stat, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code)

@@

```
We have maybe as many as 177 at least for some analyses.

Descriptions:

- "done" -- fully coded, can be used for whatever is specified in other column 
- "ES_direction" -- we don't have the direction coded 
- "ask" -- might be salvageable, but I have questions about coding
- "unusable" -- got as far as I can, and it does not have complete descriptives
- "missing" -- student didn't finish or we don't have write-up
- "non-experiment" -- student replicated something that was not an experiment
- "reproduction" -- student did a reproduction and not replication

@@

Compute prediction intervals and p_orig.

@@

d_es_predInt <- d_es |> 
  rowwise() |> 
  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
         p_orig = do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
         sub_rep = do_subjective_rep(replicated_instructor_code, 
                                     replicated_report_code, 
                                     adjudicated_replication_code))
```

@@

```{r}
d_for_model <- d_es_predInt |> 
  ungroup() |> 
  mutate(pub_year= target_year-mean(target_year),
         log_p =log(target_p_calc),
         log_sample =log(target_N),
         log_ratio_ss = log(replication_N/target_N),
         change_platform=ifelse(replication_on_turk==target_on_turk,0,1),
         #this codes 1 if the original was in person, but replication turk/prolific,
         # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
         open_data=ifelse(open_data=="yes", 1,0),
         open_mat=ifelse(open_materials=="yes", 1,0),
         stanford=ifelse(stanford_internal=="yes", 1,0),
         is_within=case_when(
           within_between=="within" ~ 1,
           within_between=="mixed" ~ 1,
           within_between=="between" ~ 0),
         log_trials=log(repeated_measure),
         predInt=as.numeric(predInt)) |> 
  select(include, target_lastauthor_year, academic_year, subfield, 
         pub_year, log_p, log_sample, log_ratio_ss, change_platform, target_d_calc,
         stanford, open_data, open_mat, 
         is_within, single_vignette, log_trials, 
         predInt, p_orig, sub_rep)

>>>>

raw <- readxl::read_xlsx(here("data","raw_data.xlsx"), 
                       sheet="aligned data", skip=1) |> select(target_lastauthor_year, sensitivity, include,
         status, status_explanation,  academic_year, journal, target_cite, article_link, study_number,  subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_raw_stat, effect_description, same_dir, replication_N,
         replication_raw_stat, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code) |> write_csv(here("data","raw_data.csv"))
```

@@

```{r}
d <- read_csv(here("data", "raw_data.csv")) |> 
  select(target_lastauthor_year, sensitivity, include,
         status, academic_year, subfield, target_year, stanford_internal, 
         open_data, open_materials, target_on_turk, replication_on_turk, 
         within_between, single_vignette, repeated_measure,
         target_N, target_raw_stat, same_dir, replication_N,
         replication_raw_stat, replicated_instructor_code, replicated_report_code,
         adjudicated_replication_code)

@@

```
Descriptions:

- "done" -- fully coded, can be used for whatever is specified in other column 
- "cannot tell direction" -- have stats for an effect, but can't tell which direction it is in
- "unusable" -- got as far as I can, and it does not have complete descriptives
- "missing" -- student didn't finish or we don't have write-up
- "non-experiment" -- student replicated something that was not an experiment
- "reproduction" -- student did a reproduction and not replication

@@

Compute prediction intervals and p_orig, write processed data to file.

@@

d_es_predInt <- d_es |> 
  rowwise() |> 
  mutate(predInt = do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
         p_orig = do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
         sub_rep = do_subjective_rep(replicated_instructor_code, 
                                     replicated_report_code, 
                                     adjudicated_replication_code)) |> write_csv(here("data","processed_data.csv"))
```

@@

```{r}
d_for_model <- d_es_predInt |> 
  ungroup() |> 
  mutate(pub_year= target_year-mean(target_year),
         log_p =log(target_p_calc),
         log_sample =log(target_N),
         log_ratio_ss = log(replication_N/target_N),
         change_platform=ifelse(replication_on_turk==target_on_turk,0,1),
         #this codes 1 if the original was in person, but replication turk/prolific,
         # 0 if they were both on turk/prolific or both in-person (rare, but happens a few times)
         open_data=ifelse(open_data=="yes", 1,0),
         open_mat=ifelse(open_materials=="yes", 1,0),
         stanford=ifelse(stanford_internal=="yes", 1,0),
         is_within=case_when(
           within_between=="within" ~ 1,
           within_between=="mixed" ~ 1,
           within_between=="between" ~ 0),
         log_trials=log(repeated_measure),
         predInt=as.numeric(predInt)) |> 
  select(include, target_lastauthor_year, academic_year, subfield, 
         pub_year, log_p, log_sample, log_ratio_ss, change_platform, target_d_calc,
         stanford, open_data, open_mat, 
         is_within, single_vignette, log_trials, 
         predInt, p_orig, sub_rep) |> write_csv(here("data","for_model.csv"))

### 2023-03-16 paper/manuscript.Rmd
work on floats

header-includes:
 - \usepackage{setspace}\singlespacing
 - \renewcommand{\textfraction}{0.00}
 - \renewcommand{\topfraction}{1}
 - \renewcommand{\bottomfraction}{1}
 - \renewcommand{\floatpagefraction}{1}
 - \setcounter{topnumber}{3}
 - \setcounter{bottomnumber}{3}
 - \setcounter{totalnumber}{4}

@@

knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
 library("papaja")
library("bookdown")
library("rticles")
 library(here)
 library(tidyverse)
library(patchwork)
 library(brms)
 library(lme4)
 library(tidybayes)
 library(mgcv)
 library(cowplot)
 library(gridExtra)
library(broom.mixed)
library(tidymv)
library(mgcViz)
library(kableExtra)
#r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")

model_location="code/models"
```

@@

```{r, eval=F}
f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1UT6KLRujn6iEQ_s01_4yNfFYqc7hAWTpB-t9mdDp0O8/edit#gid=0")
googledrive::drive_download(f, path=here("data","raw_data.xlsx"), overwrite=T)

@@

@@

Over the years, there have been a number of student projects, of these we are able to include foobar (see PRISMA). Because of variance in the experimental designs and reporting practices, we have variable statistical information. To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables. Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors. Other model results, including those from a sensitivity analysis, are available in the supplement.

>>>>

header-includes:
 - \usepackage{tikz}
 - \usetikzlibrary{positioning,chains}
 - \usepackage{setspace}\singlespacing
 - \renewcommand{\textfraction}{0.00}
 - \renewcommand{\topfraction}{1}
 - \renewcommand{\bottomfraction}{1}
 - \renewcommand{\floatpagefraction}{1}
 - \setcounter{topnumber}{3}
 - \setcounter{bottomnumber}{3}
 - \setcounter{totalnumber}{4}

@@

knitr::opts_chunk$set(echo=F, warning=F, message=F)#dev = "png", dev.args = list(type = "cairo-png")
 library("papaja")
library("bookdown")
library("rticles")
 library(here)
 library(tidyverse)
 library(brms)
library(tidybayes)
library(kableExtra)
library(viridis)
#r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")

model_location="code/models"

d <- read_csv(here("data", "processed_data.csv"))
```

@@

@@

```{=latex}
\definecolor{bad}{HTML}{FFCCCB}
		\definecolor{meh}{HTML}{efefef}
			\definecolor{good}{HTML}{abcdff}
	\tikzset{
		mynode/.style={
			draw, rectangle, align=center, text width=4.5cm, scale=1, font=\small, inner sep=.5ex},
		arrow/.style={
		 very thick,->,>=stealth}
	}

\begin{figure}[ht]

	\begin{tikzpicture}[
		node distance=.8cm,
		start chain=1 going below,
		every join/.style=arrow,
		]
		\coordinate[on chain=1] (tc);
		\node[mynode, on chain=1, fill=meh] (n2)
		{\textbf{210} projects from 2011-2022};
		\node[mynode, join, on chain=1, fill=meh] (n3)
		{\textbf{189} original - replication pairs};
		\node[mynode, join, on chain=1, fill=meh] (n4)
		{\textbf{177} experimental pairs};
		\node[mynode, join, on chain=1, fill=good] (n5)
		{\textbf{176} pairs included};
		\node[mynode, join, on chain=1, fill=good] (n6)
		{\textbf{131} pairs with ES};
		\node[mynode, join, on chain=1, fill=good] (n7)
		{\textbf{107} pairs with SMD};

		\begin{scope}[start chain=going right]
			\chainin (n2);
			\node[mynode, join, on chain, fill=bad]
			{ \textbf{2} missing projects \\ \textbf{19} reproducibility projects};
			\chainin (n3);
			\node[mynode, join, on chain, fill=bad]
			{\textbf{12} non-experimental pairs};
			\chainin (n4);
			\node[mynode, join, on chain, fill=bad]
			{\textbf{1} pair missing sample size};
		\end{scope}
	\end{tikzpicture}
\caption{Which studies were excluded for what reasons, and how many original-replication pairs are left.}\label{fig:prisma}
\end{figure}

```{r smd, out.height="25%", fig.width=5, fig.height=3, fig.pos="ht", fig.cap="TODO caption here"}
d |> 
  filter(target_d_calc < 5, rep_d_calc < 5) |>
  ggplot(aes(x=target_d_calc, y=rep_d_calc, color=sub_rep))+

  geom_abline(slope=1, intercept=0, lty = 2)+
  geom_smooth(method = "lm") + 
   geom_point(size=2.5) +
  geom_hline(yintercept = 0, lty = 2)+
  scale_color_viridis(discrete=F, direction = 1, 
                      name = "Subjective\nReplication\nSuccess\n")+
  labs(color="subrep", x="Original SMD", y="Replication SMD") + 
  theme(legend.position = "right")

```{r mod-results, out.height="25%", fig.width=5, fig.height=3, fig.pos="ht", fig.cap="TODO caption here"}
tier1_subjective <- read_rds(here(model_location, "tier1_subjective.rds"))
tier1_subjective |> 
gather_draws(`b_[a-zA-Z_(): ]+`, regex=TRUE) |> mutate(Term=str_sub(.variable, 3,-1) |> str_replace("M","_"), Estimate=.value) |> mutate(Term=factor(Term, levels=c("subfieldsocial", "subfieldother_psych", "subfieldnon_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "z_pub_year", "z_log_trials", "z_log_sample", "z_log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |> 
  ggplot(aes(y = reorder(Term, Estimate, mean), x = Estimate)) + geom_vline(xintercept=0)+
  stat_pointinterval(color="#440154")+labs(y="", x="Estimate, 66%, 95% CrI predicting subjective replication score")+theme(axis.text=element_text(size=11))

```{r}

for_cor <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |>
  select(sub_rep, 
         pub_year, subfield, open_data, open_mat, stanford, change_platform, log_ratio_ss, is_within, single_vignette, log_sample, log_trials) |> mutate(social=ifelse(subfield=="social", 1,0),other_psych=ifelse(subfield=="other-psych",1,0), non_psych=ifelse(subfield=="non-psych", 1,0)) 
sub_cor <- function(var, stat = "estimate") {
  if (stat == "estimate") {
    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$estimate
  } else {
    cor.test(for_cor$sub_rep, pull(for_cor, {{var}}))$p.value
  }
}

preds <- c("pub_year", "open_data",  "open_mat", "stanford", "change_platform", 
           "log_ratio_ss", "is_within", "single_vignette", "log_sample", 
           "log_trials", "social", "other_psych", "non_psych")

cors <- tibble(preds = preds) |>
  mutate(r = sapply(preds, function(x) sub_cor(x, stat = "estimate")),
         p = sapply(preds, function(x) sub_cor(x, stat = "p"))) |> 
  mutate(Predictors=factor(preds, levels=c("social", "other_psych", "non_psych", "is_within", "single_vignette", "change_platform", "open_data", "open_mat", "stanford", "pub_year", "log_trials", "log_sample", "log_ratio_ss"), labels=c("Social", "Other psych", "Non psych", "Within subjects", "Single vignette", "Switch to online", "Open data", "Open materials", "Stanford", "Publication year", "Log trials", "Log original sample size", "Log rep/orig sample"))) |> arrange(r) |> select(Predictors, r, p)

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc',format="latex", position="!h", caption="TODO the correlation of individual predictors with subjective replication outcomes. For subfield, cognitive psychology is treated as the baseline condition.") |> kable_styling(full_width=F, font_size=10)

```{r}
dat <- read_csv(here("data","for_model.csv")) |> filter(include %in% c("stats", "exp", "pred_int")) |> mutate(sub_rep=as.factor(sub_rep))

sub_with_leg <- dat |> mutate(subfield=factor(subfield, levels=c("cognitive", "social", "other-psych", "non-psych"), 
                                              labels=c("Cognitive\npsychology", "Social\npsychology", "Other\npsychology", "Not\npsychology"))) |>
  ggplot(aes(x=subfield, fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank())+
  labs(y="Count", fill="Subjective \n replication \n score")

leg <- get_legend(sub_with_leg)

subfield <- sub_with_leg+theme(legend.position="none")

open <- dat |> mutate(openness=case_when(
  open_mat==1& open_data==1 ~ "Open materials \n Open data",
  open_mat==1 ~ "Open materials \n No open data",
  open_data==1 ~ "No open materials \n Open data",
  T ~ "No open materials \n No open data")) |> 
  ggplot( aes(x=openness |> factor(), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
  labs(y="Count")

modal <- ggplot(dat, aes(x=ifelse(change_platform,"Switch to online","Same modality"), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
  labs(y="Count")

within <- ggplot(dat, aes(x=ifelse(is_within, "Within", "Between"), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
  labs(y="Count")

vignette <- ggplot(dat, aes(x=ifelse(single_vignette, "Single vignette", "Multiple vignettes"), fill=sub_rep))+
  geom_bar(stat="count", position="dodge")+
  scale_fill_viridis(discrete=T)+
  theme(axis.text=element_text(size=14), axis.title=element_text(size=14), axis.title.x=element_blank(), legend.position="none")+
  labs(y="Count")

top_row <- plot_grid(subfield, modal, leg, rel_widths=c(1,.5,.5), nrow=1)
mid_row <- plot_grid(open, within, vignette, rel_widths=c(1,.5,.5), nrow=1)
plot_grid (top_row, mid_row, nrow=2)
```

@@

Over the years, there have been a number of student projects, of these we are able to include foobar (see Figure \ref{fig:prisma}). Because of variance in the experimental designs and reporting practices, we have variable statistical information. To address this, we conducted a series of models, balancing between including as many data points as possible, and including potentially relevant outcome and predictor variables. Here we focus on one set of models, the prediction of subjective replication outcome on the basis of the whole dataset without the statistical predictors. Other model results, including those from a sensitivity analysis, are available in the supplement.
